Using spatially biased variables in ecosystem condition accounting with a GIS based workflow

### 2024-02-22 manuscript/HIAs.qmd
forest plot v1

```{r forets plot}
# Forest plot
# https://stackoverflow.com/questions/58657802/forest-plot-with-subgroups-in-ggplot2
```

>>>>

```{r forets plot}
# Forest plot
# https://stackoverflow.com/questions/58657802/forest-plot-with-subgroups-in-ggplot2
# 
# #define colours for dots and bars
barCOLS = c("grey80","grey60", "grey40", "grey20")
dotCOLS = c("grey90","grey70", "grey50", "grey40")

stats_tbl |>
  ggplot(aes(x=Municipality, 
             y=mean, 
             ymin=mean-sd, 
             ymax=mean+sd,
             col=factor(infrastructureIndex),
             fill=factor(infrastructureIndex))) + 
#specify position here
  geom_linerange(
    size=5,
    position=position_dodge(width = .9)) +
  #geom_hline(yintercept=1, lty=2) +
#specify position here too
  geom_point(
    size=3, 
    shape=21, 
    colour="white", 
    stroke = 0.5,
    position=position_dodge(width = .9)) +
  scale_fill_manual(values=barCOLS)+
  scale_color_manual(values=dotCOLS)+
  scale_x_discrete(name="") +
  scale_y_continuous(name="Indicator values", limits = c(0, 1)) +
  coord_flip() +
  theme_bw() +
  labs(fill = "HIA",
       col = "HIA") +
  facet_wrap(.~indicator,
             ncol=1)
```
